Public Opinions on Sexual Education in Public Schools

### 2024-03-19 paper/paper.qmd
Improve abstracts and figure captions

---
title: "Public Opinions on Sexual Education in Public Schools"
subtitle: "An Analysis of Political, Educational, and Generational Influences in the United States from 1972 to 2022"
author: 
  - Wanling Ma
thanks: "Code and data are available at: https://github.com/WanlingMa/Favor-or-oppose-sex-education-in-public-schools"
date: today
date-format: long
abstract: "This paper examines the public's views on sexual education in U.S. public schools, drawing on data from the General Social Survey (GSS). Our analysis reveals that the support for sexual education varies significantly by political ideology, education level, and age, with Democrats, the highly educated, and younger people being the most supportive. These variations underscore the deep correlation between individual traits and attitudes towards sexual education, reflecting broader societal debates. In conclusion, the study highlights the critical role of inclusive perspectives in developing sexual education policies, suggesting that such education could serve as a unifying tool for public health and societal welfare."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-sexeduc-vs-ages
#| fig-cap: "Respondents' Opinions on Sexual Education in Public School versus Respondents' Ages Over 1974 - 2022"

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-sexeduc-vs-degree
#| fig-cap: "Respondents' Opinions on Sexual Education in Public School versus Respondents' Highest Degree Over 1974 - 2022"

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-sexeduc-vs-partyid
#| fig-cap: "Respondents' Opinions on Sexual Education in Public School versus Respondents' Highest Degree Over 1974 - 2022"

>>>>

---
title: "Public Opinions on Sexual Education in Public Schools"
subtitle: "An Analysis of Political, Educational, and Generational Influences in the United States from 1972 to 2022"
author: 
  - Wanling Ma
thanks: "Code and data are available at: https://github.com/WanlingMa/Favor-or-oppose-sex-education-in-public-schools"
date: today
date-format: long
abstract: "This paper examines the public's views on sexual education in U.S. public schools, drawing on data from the General Social Survey (GSS). Our analysis shows that differences in support for sexual education are marked by political ideology, education level, and age, with Democrats, the highly educated, and younger people showing the most support. These variations underscore the deep correlation between individual traits and attitudes towards sexual education, reflecting broader societal debates. Ultimately, the study highlights the critical role of inclusive perspectives in developing sexual education policies, suggesting that such education could serve as a unifying tool for public health and societal welfare."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-sexeduc-vs-ages
#| fig-cap: "Trends of Respondents' Opinions on Sexual Education in Public School versus Respondents' Ages Over 1974 - 2022"

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-sexeduc-vs-degree
#| fig-cap: "Trends of Respondents' Opinions on Sexual Education in Public School versus Respondents' Highest Degree Over 1974 - 2022"

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-sexeduc-vs-partyid
#| fig-cap: "Trends of Respondents' Opinions on Sexual Education in Public School versus Respondents' Highest Degree Over 1974 - 2022"
